Language Bias in a Multilingual Tweet Corpus

### 2018-06-27 paper.tex
Language uniformity

@@

\input{figures/topic_lang_counts.tex}

@@

\input{figures/topic_timeline.tex}

>>>>

The Language uniformity score is defined in \cite{milajevs:2017:BUCC}. It is the normalized number of tweets in the most frequent language. Figure~\ref{fig:uniformity_score} compares the language uniformity scores of active users in this work and in \cite{milajevs:2017:BUCC}. Apart of the higher number of active users in this work (which is expected, as the corpus covers a longer period), the currently presented corpus has more active users with the language uniformity score about 0.5. Even though the majority is mostly monoligual, this work captured more (at least) bilingual users.

\input{figures/uniformity_score.tex}

@@

\input{figures/topic_lang_counts.tex}
\input{figures/topic_timeline.tex}

@@
